Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-09 thesis.Rmd
ny struktur och lite mer text

## Participants
There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excluded` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

## Descriptive data
The study demographic median age is ... and the most common gender is male, `r male`.

@@

### BE classification
For the outcome OFI, out of the `r sample` patients reviewed, `r ofi` patients had a positive OFI. Clinically, the

### SBP classification

Table 3 present the sample characteristics.

Table 4 present

>>>>

## Participants
There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excludednum` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

@@

```{r sample-characteristics, echo=FALSE}
sample.characteristics.table
```

## Descriptive data

### BE classification
The study demographics median age is `r age` and the most common gender is male, `r male`. Clinically, the median ISS is (...) which is class (...), median INR is (...), and the most common Preinjury ASA class is (...), at (...)%.

```{r sample-characteristics BE, echo=FALSE}
sample.characteristics.tableBE
```
### SBP classification
The study demographics median age is `r age` and the most common gender is male, `r male`. Clinically, the median ISS is (...) which is class (...), median INR is (...), and the most common Preinjury ASA class is (...), at (...)%.

Table 3, 4, 5 present the sample characteristics.

```{r sample-characteristics SBP, echo=FALSE}
sample.characteristics.tableSBP
```

## Outcome data
Out of the `r sample` patients reviewed, `r ofi` patients had at least one positive OFI.

The most common

Table 6 and 7 present sub-ofi broad

```{r BE-subofi, echo=FALSE}
print(p)
```

```{r SBP-subofi, echo=FALSE}
print(pSBP)
```

Table 8 and 9 present sub-ofi detailed

```{r SBP-subofi-detailed, echo=FALSE}
print(pd)
```

```{r BE-subofi-detailed, echo=FALSE}
print(pSBPd)
```

Table 10 and 11 adjusted log
```{r Adjusted_log, echo=FALSE}
log_regBE_sample.characteristics.table
log_regSBP_sample.characteristics.table
```

Table 12 and 13 unadjusted log
```{r Unadjusted_log, echo=FALSE}
log_regBE_sample.characteristics.table_unadjusted
log_regSBP_sample.characteristics.table_unadjusted
```
